---
title: "PEC 422/2014 ENTRY CONTENT<br/>
Proposal for amendment to the Constitution<br/>

Situation Ready for agenda in plenary (Plen)<br/>

Proposition Identification"
output: github_document
---

## Tree folder and files 

```{r tree}
# .
# ├── ccjc.png
# ├── ccp.png
# ├── doc-learn-pec244%2014.Rproj
# ├── license
# ├── matrix
# │   └── gnu
# │       ├── bin
# │       │   ├── i.R
# │       │   ├── ricd.R
# │       │   └── table.R
# │       ├── image
# │       ├── lib
# │       │   └── ccjc.R
# │       └── test
# │           └── ccp.R
# ├── readme_files
# │   └── figure-gfm
# │       ├── ccjc-1.png
# │       ├── ccp-1.png
# │       └── ricd-1.png
# ├── readme.md
# ├── readme.Rmd
# └── ricd.png

```
## bit::bit-demo demo of the bit package

```{r i}
#!/usr/bin/r

## ---- echo = FALSE, results = "hide", message = FALSE-------------------------
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
require(bit)
.ff.version <- try(packageVersion("ff"), silent = TRUE)
.ff.is.available <- !inherits(.ff.version, "try-error") && .ff.version >= "4.0.0" && require(ff)
#tools::buildVignette("vignettes/bit-demo.Rmd")
#devtools::build_vignettes()

## -----------------------------------------------------------------------------
n <- 1e8
b1 <- bit(n)
b1

## -----------------------------------------------------------------------------
object.size(b1)/n

## -----------------------------------------------------------------------------
b1[10:30] <- TRUE
summary(b1)

## -----------------------------------------------------------------------------
b2 <- bit(n)
b2[20:40] <- TRUE
b2

## -----------------------------------------------------------------------------
b1 & b2

## -----------------------------------------------------------------------------
summary(b1 & b2)

## -----------------------------------------------------------------------------
w1 <- as.bitwhich(b1) 
w2 <- as.bitwhich(b2)
object.size(w1)/n

## -----------------------------------------------------------------------------
w1 & w2

## -----------------------------------------------------------------------------
summary(w1 & w2)

## -----------------------------------------------------------------------------
summary(b1 & w2)

## -----------------------------------------------------------------------------
summary(b1, range=c(1,1000))

## -----------------------------------------------------------------------------
as.which(b1, range=c(1, 1000))

## -----------------------------------------------------------------------------
lapply(chunk(from=1, to=n, length=10), function(i)as.which(b1, range=i))

## ---- eval=.ff.is.available---------------------------------------------------
options(ffbatchbytes=1024^3)
x <- ff(vmode="single", length=n)
x[1:1000] <- runif(1000)
lapply(chunk(x, length.out = 10), function(i)sum(x[as.hi(b1, range=i)]))

## ---- eval=.ff.is.available---------------------------------------------------
delete(x)
rm(x, b1, b2, w1, w2, n)


```

## Available methods

```{r table}
#!/usr/bin/r

## ----setup, include = FALSE---------------------------------------------------
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

## ----echo = FALSE, message = FALSE--------------------------------------------
library(broom)
library(dplyr)
library(stringr)

method_df <- function(method_name) {
  m <- as.vector(methods(method_name))
  tibble::tibble(class = str_remove(m, str_c(method_name, "[.]")),
                 !!method_name := "x")
}

method_df("tidy") %>% 
  left_join(method_df("glance")) %>% 
  left_join(method_df("augment")) %>% 
  mutate_all(tidyr::replace_na, "") %>% 
  knitr::kable()

```

R Markdown with the Docco Classic Style
This is an example of Markdown vignettes using the Docco style.

Docco
To use the Docco style for Markdown vignettes in an R package, you need to

add *.Rmd files under the vignettes directory
add Suggests: knitr and Vignette Builder: knitr to the DESCRIPTION file
specify the vignette engine \VignetteEngine{knitr::docco_classic} in the Rmd files (inside HTML comments)
After building and installing the package, you can view vignettes via

browse Vignettes(package = 'Your_Package')
¶
Examples
Below are some code chunks as examples.

cat('_hello_ **markdown**!', '\n')
¶
hello markdown!

Normally you do not need any chunk options.

1+1
## [1] 2
10:1
##  [1] 10  9  8  7  6  5  4  3  2  1
rnorm(5)^2
## [1] 0.26160 0.04578 0.03464 0.01449 1.02583
strsplit('hello, markdown vignettes', '')
## [[1]]
##  [1] "h" "e" "l" "l" "o" "," " " "m" "a" "r" "k" "d" "o" "w" "n" " " "v" "i" "g"
## [20] "n" "e" "t" "t" "e" "s"
¶
Feel free to draw beautiful plots and write math 
¶
plot of chunk unnamed-chunk-2

n=300; set.seed(123)
par(mar=c(4,4,.1,.1))
plot(rnorm(n), rnorm(n), pch=21, cex=5*runif(n), col='white', bg='gray')
¶
How does it work
The markdown package (>= v0.6.2) supports custom HTML templates, and the docco engine in knitr uses a custom template to compile Markdown to HTML:

head(knitr::rocco, 5)
##                                                                                    
## 1 function (input, ...)                                                            
## 2 {                                                                                
## 3     out = knit2html(input, ..., meta = list(css = system.file("misc",            
## 4         "docco-classic.css", package = "knitr")), template = system.file("misc", 
## 5         "docco-classic.html", package = "knitr"))
¶
That is it.

You probably have noticed that you can adjust the widths of the two columns using your cursor. What is more, press T on your keyboard, and see what happens.
```{r ccjc}

#!/usr/bin/r
## ----hello, results='asis'----------------------------------------------------
cat('_hello_ **markdown**!', '\n')

## -----------------------------------------------------------------------------
1+1
10:1
rnorm(5)^2
strsplit('hello, markdown vignettes', '')

## -----------------------------------------------------------------------------
n=300; set.seed(123)
par(mar=c(4,4,.1,.1))
plot(rnorm(n), rnorm(n), pch=21, cex=5*runif(n), col='white', bg='gray')

## -----------------------------------------------------------------------------
head(knitr::rocco, 5)


```

```{r ccp}
#!/usr/bin/r

## ----hello, results='asis'----------------------------------------------------
cat('_hello_ **markdown**!', '\n')

## -----------------------------------------------------------------------------
1+1
10:1
rnorm(5)^2
strsplit('hello, markdown vignettes', '')

## -----------------------------------------------------------------------------
n=300; set.seed(123)
par(mar=c(4,4,.1,.1))
plot(rnorm(n), rnorm(n), pch=21, cex=5*runif(n), col='white', bg='gray')

## ----header, eval=FALSE-------------------------------------------------------
#  knit2html(..., template = system.file('misc', 'docco-template.html', package='knitr'))
```


numericDeriv {stats}	R Documentation
Evaluate Derivatives Numerically
Description
numericDeriv numerically evaluates the gradient of an expression.

Usage
numericDeriv(expr, theta, rho = parent.frame(), dir = 1,
             eps = .Machine$double.eps ^ (1/if(central) 3 else 2), central = FALSE)
Arguments
expr	
expression or call to be differentiated. Should evaluate to a numeric vector.

theta	
character vector of names of numeric variables used in expr.

rho	
environment containing all the variables needed to evaluate expr.

dir	
numeric vector of directions, typically with values in -1, 1 to use for the finite differences; will be recycled to the length of theta.

eps	
a positive number, to be used as unit step size h for the approximate numerical derivative (f(x+h)-f(x))/h or the central version, see central.

central	
logical indicating if central divided differences should be computed, i.e., (f(x+h) - f(x-h)) / 2h . These are typically more accurate but need more evaluations of f().

Details
This is a front end to the C function numeric_deriv, which is described in Writing R Extensions.

The numeric variables must be of type double and not integer.

Value
The value of eval(expr, envir = rho) plus a matrix attribute "gradient". The columns of this matrix are the derivatives of the value with respect to the variables listed in theta.

Author(s)
Saikat DebRoy saikat@stat.wisc.edu; tweaks and eps, central options by R Core Team.

Examples
```{r ricd}
#!/usr/bin/r

myenv <- new.env()
myenv$mean <- 0.
myenv$sd   <- 1.
myenv$x    <- seq(-3., 3., length.out = 31)
nD <- numericDeriv(quote(pnorm(x, mean, sd)), c("mean", "sd"), myenv)
str(nD)

## Visualize :
require(graphics)
matplot(myenv$x, cbind(c(nD), attr(nD, "gradient")), type="l")
abline(h=0, lty=3)
## "gradient" is close to the true derivatives, you don't see any diff.:
curve( - dnorm(x), col=2, lty=3, lwd=2, add=TRUE)
curve(-x*dnorm(x), col=3, lty=3, lwd=2, add=TRUE)
##
## IGNORE_RDIFF_BEGIN
# shows 1.609e-8 on most platforms
all.equal(attr(nD,"gradient"),
          with(myenv, cbind(-dnorm(x), -x*dnorm(x))))
## IGNORE_RDIFF_END

```
